MassWateR: Improving quality control, analysis, and sharing of water quality data

### 2023-07-13 paper.Rmd
edited acknowledgments

This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bay Estuary Partnership. We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.

>>>>

This work was supported by an Exchange Network grant from the US Environmental Protection Agency awarded to the Massachusetts Bays National Estuary Partnership. We thank the early users of \CRANpkg{MassWateR} that contributed ideas on improving the package during initial testing.  We are grateful for discussions with the Massachusetts Department of Environmental Protection that guided the presentation of results in the quality control assessments.
